Wolbachia, Toxoplasma and O. Cordyceps: Extreme Host-Manipulating Microbes That Are Changing the World

### 2015-12-16 paper.tex
Finished impacts for Wolbachia. Also changed the title a bit

\title{Wolbachia, Toxoplasma and O. Cordyceps: Extreme Host-Manipulating Microbes That Changed the World}
    \author{C. Bekins, R. Chapman and B. Wasti}
    \date{December 2015}
    \maketitle

@@

The usage of the relationship between \textit{Wolbachia} and its host may even be abused in other ways.

\section*{Analysis}

>>>>

\title{Wolbachia, Toxoplasma and O. Cordyceps: Extreme Host-Manipulating Microbes That Are Changing the World}
    \author{C. Bekins, R. Chapman and B. Wasti}
    \date{December 2015}
    \maketitle

@@

The abuse of the relationship between \textit{Wolbachia} and its host may also be done in the opposite way. A species infected with \textit{Wolbachia} becomes dependant on \textit{Wolbachia}. If the \textit{Wolbachia} were to be killed off, say by antibiotics, then the host would struggle to survive. This idea can be used to treat filarial infections in humans: targetting the \textit{Wolbachia} kills off the filaraea.\cite{wolbachia}

Although this technique is rather new and is not widely used yet, it has potential to be a whole new route by which we can treat filarial infections. By combining antiwolbachia medication with antifilarial treatments, there is twice the potential to successfully cure the infection. Through studying \textit{Wolbachia}, we can save lives.
